---
title: "p8105_hw1_jw4690"
output: github_document
date: "2024-09-12"
author: "Jingxi Wang"
---

```{r}
library(tidyverse)
```


## Problem 1

```{r penguins}

library(palmerpenguins)

data("penguins", package = "palmerpenguins")
```

The key variables are `species`, `island`, `bill_length_mm`, `bill_depth_mm`, `flipper_length_mm`, `body_mass_g`, `sex`, and `year`.

The penguins dataset has `r nrow(penguins)` rows, `r ncol(penguins)` columns.

The mean of the flipper length is `r mean(penguins$flipper_length_mm, na.rm = TRUE)` mm.

```{r scatterplot}

ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm, color = species)) + geom_point() 

ggsave("penguins_scatterplot.png", device = "png")
```


## Problem 2

```{r}

p2_df = 
  tibble(
    sample_normal_dis = rnorm(10),
    logical_vector = rnorm(10) > 0,
    character_vector = letters[1:10],
    factor_vector = factor(rep(c("Lv1", "Lv2", "Lv3"), length.out = 10))
  )
```

```{r, warning = FALSE}
mean(pull(p2_df, var = sample_normal_dis, name = NULL))

mean(pull(p2_df, var = logical_vector, name = NULL))

mean(pull(p2_df, var = character_vector, name = NULL))

mean(pull(p2_df, var = factor_vector, name = NULL))
```

The sample normal distribution and the logical vector work, the character vector and factor vector do not work.

```{r, eval = FALSE}
mean(as.numeric(pull(p2_df, var = logical_vector, name = NULL)))

mean(as.numeric(pull(p2_df, var = character_vector, name = NULL)))

mean(as.numeric(pull(p2_df, var = factor_vector, name = NULL)))
```

For logical vector, use `as.numeric` will converts logical value `TRUE` and `FALSE` to 1 and 0, so we can take the mean of the logical vector. 

For character vector, `as.numeric` cannot converts characters to numbers, so we cannot take the mean of the character vectors.

For factor vector, `as.numeric` can converts the levels to their underlying integer codes, but these values may not carry any meaningful numeric interpretation. 

This explains why taking the mean of logical and factor variables can work, while for character variables it fails, as they cannot be coerced to numbers.



